Efficient ancestry and mutation simulation with msprime 1.0

### 2021-11-25 response-to-reviewers.tex

Torres et al. 2020. The temporal dynamics of background selection in
nonequilibrium populations. Genetics.

Johri et al. 2021. The impact of purifying and background selection on the
inference of population history: problems and prospects. MBE.

Murphy et al. 2021. Broad-scale variation in human genetic diversity levels is
predicted by purifying selection on coding and non-coding elements. bioRxiv.
\end{point}

\begin{reply}
We have added a cautionary paragraph at the end of the introduction, noting that
neutral simulations are an approximation, which often do not accurately
reflect biological reality. However, as we have argued above, major methodological
advances of the type that you discuss (which we agree are extremely important!)
are beyond the scope of the current manuscript.
\end{reply}

### 2021-11-26 response-to-reviewers.tex

Torres et al. 2020. The temporal dynamics of background selection in
nonequilibrium populations. Genetics.

Johri et al. 2021. The impact of purifying and background selection on the
inference of population history: problems and prospects. MBE.

Murphy et al. 2021. Broad-scale variation in human genetic diversity levels is
predicted by purifying selection on coding and non-coding elements. bioRxiv.
\end{point}

\begin{reply}
We agree that neutral simulations are drastic approximations, and (as with all
null models) care needs to be exercised in their interpretation and use. We
have added text to the introduction to emphasise this point. However, as we
have argued above, major methodological advances of the type that you discuss
(which we agree are extremely important!) are beyond the scope of the current
manuscript. While the question of how to best approximate background selection
in a coalescent framework is a topic of ongoing research (e.g. Nicolaisen \&
Desai 2013, Zeng \& Charlesworth 2011), we would argue that the long term
ambition of simulating ancestry under more realistic non-neutral null models
(e.g. condition on maps of background selection) only makes sense if such
simulations are both efficient and can be embedded in realistic models of other
biological processes, many of which we have implemented in this version of
msprime.
\end{reply}

### 2021-11-26 paper.tex
Konrad's edites

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular the existence of pervasive background
selection in many
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}
means that care must be taken to ensure that the results of
neutral simulations are appropriate for the study in question.

>>>>

The efficiency of coalescent simulations depends
crucially on the assumption of neutrality, and it is important
to note that there are many situations in which this will be a poor approximation
of biological reality~\citep{johri2021statistical}.
In particular, background selection has been shown to affect genomewide
sequence variation in a wide range of
species~\citep{charlesworth1993effect,charlesworth1995pattern,charlesworth2021effects}.
Thus care must be taken to ensure that the results of neutral simulations are
appropriate for the question and genomic partition under study.
